A Real-Time Sonar Simulator for Automatic Target Recognition

### 2019-05-05 Simulator/bio/jo_inge_buskenes_new.tex
2019-05-04

His industry experience includes development of digital electronics at the European Organization for Nuclear Research (CERN), Geneva, Switzerland (2007-2008). He has lectured in digital signal processing at the Gj\o{}vik College University (2009), and at the University of Oslo (2010-2013). Current affiliation is with The Norwegian Defence Research Establishment, Kjeller, Norway, for which he is developing radar systems (2015-), and formerly sonar systems (2009, 2013).

>>>>

His industry experience includes development of digital electronics at the European Organization for Nuclear Research (CERN), Geneva, Switzerland (2007-2008). He has lectured in digital signal processing at the Gj\o{}vik College University (2009), and at the University of Oslo (2010-2013). Current affiliation is with The Norwegian Defence Research Establishment, Kjeller, Norway, where he develops sonar and radar systems.
